\section*{Exercise 2} % (fold)
\label{sec:section_name}

We want to check whether all distance functions $d_n, \forall n \in \{1,2,3\}$ are distance measures by verifying each of the 
following properties:

\begin{itemize}
	\item $d(x,y)=0 <=> x=y$
	\item $d(x,y) = d(y,x)$
	\item $d(x,y) \leq d(x,z) + d(z,y)$
\end{itemize}

If all properties are fulfilled, the distance function is called a distance measure.
After we will see which of the distance measures is shift, rotation or scale invariant.
\subsection*{i)} % (fold)
\label{sub:i}

Let's check all properties for $d_1: \mathbb{R} \times \mathbb{R} \to \mathbb{R}, d_1(x,y) = |x^2 - y^2|$:

\subsubsection*{zero distance} % (fold)
\label{ssub:zero_distance}
\[
d_1(-3,3) = |(-3)^2 - 3^2| = 0, \text{ but } x \neq y
\]

% subsubsection zero_distance (end)

\subsubsection*{symmetry} % (fold)
\label{ssub:symmetry}

\[
d_1(y,x) = |y^2 - x^2| = |-(x^2 - y^2)| = |x^2 - y^2|
\]

% subsubsection symmetry (end)

\subsubsection*{triangle inequality} % (fold)
\label{ssub:triangle_inequality}

\[
d_1(x,y) = |x^2 - y^2| = |x^2 - z^2 + z^2 - y^2|.
\] 
Let's define:
\[
a,b \in \mathbb{R}: a = x^2 - z^2, b = z^2 - y^2. 
\]
Using the triangle inequality, we know that 
\[
|a| + |b| \geq |a+b| <=> |x^2 - y^2| \leq |x^2 - z^2| + |z^2 - y^2|
\]

Since the ``zero distance'' property is not fulfilled, \textbf{$d_1$ is not 
a distance measure}.
% subsubsection triangle_inequality (end)

% subsection i (end)

\subsection*{ii)} % (fold)
\label{sub:ii}

Let's check all properties for $d_2: \left[0,\pi\right]^D \times \left[0,\pi\right]^D \to \mathbb{R}$
and $d_2(x,y) = \sqrt{\sum_{i=1}^{D}(cos(x_i)-cos(y_i))^2}$:

\subsubsection*{zero distance} % (fold)
\label{ssub:zero_distance}
Let's define $a_i := (cos(x_i) - cos(y_i))^2$. Since $a_i \geq 0$, it is obvious that $\sum_{i=1}^{D}a_i = 0 <=> a_i = 0, \forall i \in \{1,...,D\}$.
Since $f(x) = cos(x)$ is a strictly monotonic function over the interval $\left[0,\pi\right]$, we can conclude 
that $cos(x_i)-cos(y_i) = 0 <=> x_i = y_i$. Hence the distance function fulfills the ``zero distance'' property.

% subsubsection zero_distance (end)

\subsubsection*{symmetry} % (fold)
\label{ssub:symmetry}

\begin{align}
    d_2(y,x) &= \sqrt{\sum_{i=1}^{D}(cos(y_i)-cos(x_i))^2}\\
     &= \sqrt{\sum_{i=1}^{D}(-1)^2(cos(x_i)-cos(y_i))^2}\\
     &= \sqrt{\sum_{i=1}^{D}(cos(x_i)-cos(y_i))^2}\\
     &= d_2(x,y)
\end{align}

We can see that symmetry is fulfilled.

% subsubsection symmetry (end)

\subsubsection*{triangle inequality} % (fold)
\label{ssub:triangle_inequality}

To prove the triangle inequality in this case, 
we will use the cauchy-schwarz inequality for vectors
which is as follows \href{https://en.wikipedia.org/wiki/Cauchy%E2%80%93Schwarz_inequality}{\textit{\underline{Cauchy-Schwarz}}}:
\[
|\sum_{i=1}^{n}u_iv_i|^2 \leq |\sum_{i=1}^{n}u_i|^2|\sum_{i=1}^{n}v_i|^2.
\] 

The function $f(x) = \sqrt(x), \forall x \geq 0$ is a monotonic function and thus:

\[
|\sum_{i=1}^{n}u_iv_i| \leq |\sum_{i=1}^{n}u_i||\sum_{i=1}^{n}v_i|.
\] 

Now we define the $L^2$-Norm as: $||\text{\textbf{a}}|| := \sqrt(|\sum_{i=1}^{n}a_ia_i|))$, $\text{\textbf{a}}$ as the vector a and $\text{\textbf{ab}} = \sum_{i=1}^{n}a_ib_i$
as the vector product. 

\textbf{Note:} If we have a scalar in the norm: 
\[
||\text{\textbf{ab}}|| = ||a_1b_1 + a_2b_2 + ... + a_nb_n|| = \sqrt((a_1b_1 + a_2b_2 + ... + a_nb_n)^2) = a_1b_1 + a_2b_2 + ... + a_nb_n
\]

We show that:

\begin{align}
||\text{\textbf{x} + \textbf{y}}||^2 &= (\textbf{x} + \textbf{y})(\textbf{x} + \textbf{y}) \\
			&= ||\text{\textbf{x}}||^2 + 2(\textbf{x}\textbf{y}) + ||\text{\textbf{y}}||^2 \\
			& \leq ||\text{\textbf{x}}||^2 + 2||\text{\textbf{xy}}|| + ||\text{\textbf{y}}||^2 \\
\text{(using Cauchy-Schwarz)} &\leq ||\text{\textbf{x}}||^2 + 2||\textbf{x}||||\textbf{y}|| + ||\text{\textbf{y}}||^2\\
			&= (||\text{\textbf{x}}|| + ||\text{\textbf{y}}||)^2
\end{align}

So:

\begin{equation}
||\text{\textbf{x} + \textbf{y}}|| \leq ||\text{\textbf{x}}|| + ||\text{\textbf{y}}||
\end{equation}

Applying the inequality to our case:

\begin{align}
d_2(x,y) &= ||cos(\text{\textbf{x}}) - cos(\text{\textbf{y}})|| \text{ whereas } n = D \\
	   &= ||cos(\text{\textbf{x}}) - cos(\text{\textbf{z}}) + cos(\text{\textbf{z}}) - cos(\text{\textbf{y}})|| \\
(\text{using (10)})	   & \leq ||cos(\text{\textbf{x}}) - cos(\text{\textbf{z}})|| + ||cos(\text{\textbf{z}}) - cos(\text{\textbf{y}})|| \\
	   &= d_2(x,z) + d_2(z,y)
\end{align}
 
We see that all properties are fulfilled, hence \textbf{$d_2$ is 
a distance measure}.
% subsubsection triangle_inequality (end)

% subsection ii (end)

\subsection*{iii)} % (fold)
\label{sub:iii}

Let's check all properties for $d_3: \mathbb{R}^D \times \mathbb{R}^D \to \mathbb{R}$
and $d_3(x,y) = \sum_{i=1}^{D}|x_{i}-y_{i}|^3$:

\subsubsection*{zero distance} % (fold)
\label{ssub:zero_distance}
It is fairly easy to see that the only way that $\sum_{i=1}^{D}|x_{i}-y_{i}|^3 = 0$ is when $x_i = y_i, \forall i \in \{1,...,D\}$.
Therefore $d_3(x,y) = 0 <=> x=y$ and the ``zero distance'' property is fulfilled. 

% subsubsection zero_distance (end)

\subsubsection*{symmetry} % (fold)
\label{ssub:symmetry}

\begin{align}
    d_3(y,x) &= {\sum_{i=1}^{D}|y_i - x_i|^3}\\
     &= {\sum_{i=1}^{D}|-(x_i - y_i)|^3}\\
     &= {\sum_{i=1}^{D}|x_i - y_i|^3}\\
     &= d_3(x,y)
\end{align}

We can see that symmetry is fulfilled.

% subsubsection symmetry (end)

\subsubsection*{triangle inequality} % (fold)
\label{ssub:triangle_inequality}

We can easily show that the triangle inequality does not hold true for $d_3$.
Let's assume that $D=1, x_1 = 7, y_1 = 3, z_1 = 5$.
So we have:

\[
d_3(x,y)= |7 - 3|^3 = 64 > 16 = |7-5|^3 + |5-3|^3 = d_3(x,z) + d_3(z,y)
\]

Thus $d_3(x,y) \leq d_3(x,z) + d_3(z,y)$ does not hold true. 
 
We see that not all the properties are fulfilled and consequently \textbf{$d_3$ is 
not a distance measure}.
% subsubsection triangle_inequality (end)

% subsection iii (end)

\subsection*{Note} % (fold)
\label{sub:note}

In case I falsely understood the question and it is in fact asked to verify the metric properties like shift invariance, rotation 
invariant and scale invariant, we can state that: 

Since (i) and (iii) are no distance measures, it is not necessary to check for these properties. 
(ii) is neither shift, nor rotation, nor scale invariant.

% subsection note (end)

% section section_name (end)
